\chapter*{How to read this handbook}
\addcontentsline{toc}{chapter}{How to read this handbook}

\section*{Purpose of This Handbook}
\addcontentsline{toc}{section}{Purpose of This Handbook}

The primary purpose of this handbook is to faciliate interdisciplinary learning by organizing retinal imaging knowledge into a structured knowledge base. Rather than providing definitive answers or isolated facts, this handbook emphasizes the relationships among biological concepts, clinical reasoning, biomedical terminology, and computational methods. By progressively connecting these concepts, the handbook aims to help readers develop a coherent understanding of retinal imaging research, allowing them to interpret scientific literature, communicate across disciplines, and conduct evidence-informed research.

\section*{Scope}
\addcontentsline{toc}{section}{Scope}

This handbook focuses on the foundational concepts required to understand retinal imaging research from both biomedical and computational perspectives. This edition focuses primarily on color fundus photography (CFP), retinal microvasculature, retinal biomarkers, and their applications in systemic diseases, particularly stroke and atheroclerosis. To maintain conceptual consistency, this handbook prioritizes depth over breadth, focusing on concepts that form the foundation of retinal imaging research.

Future editions will progressively expand the handbook to include additional retinal imaging modalities, including optical coherence tomography (OCT), OCT angiography (OCTA), and fluorescein angiography (FA), together with multimodal retinal imaging, foundation models, and emerging computational approaches for retinal image analysis. Future editions will also explore the relationships between retinal imaging and systemic diseases, including diabetes, hypertension, and neurodegenerative disorders.

As retinal imaging research continues to evolve, the scope of this handbook will be updated accordingly to incorporate emerging scientific evidence and technological advances.

\section*{Organization of This Handbook}
\addcontentsline{toc}{section}{Organization of This Handbook}

The handbook is organized around concepts rather than individual research papers or algorithms. Each chapter introduces a coherent group of related concepts, allowing readers to progressively build an integrated understanding of retinal imaging research. Follow that, each concept is presented using a consistent structure, including a definition, biological background, clinical relevance, computational relevance, related terminology, and suggested readings. This standardized organization allows readers to easily navigate different topics efficiently while maintaining conceptual continuity throughout the handbook.

Glossary terms and cross-references are provided throughout the handbook to encourage connections between related concepts rather than isolated memorization. Selected references are also included to guide readers towards the original scientific evidence and support further exploration of each topic. 

\section*{How to Use This Handbook}
\addcontentsline{toc}{section}{How to Use This Handbook}

To obtain the greatest benefit from this handbook, readers are encouraged to approach the material with an interdisciplinary mindset, integrating perspectives from biology, medicine, and computational sciences. Although the chapters are organized sequentially to facilitate progressive learning, individual chapters and concepts may also be consulted independently through the glossary and cross-references.

\begin{table}[h]
    \centering
    \caption{Recommended Reading Pathways}
    \begin{tabularx}{\textwidth}{lX}
        \toprule
        \textbf{Reader} & \textbf{Suggested Approaches} \\
        \midrule
        AI researchers & Focus on biological background, clinical relevance, and retinal biomarkers before studying computational methods. \\
        Biomedical researchers & Begin with retinal anatomy and microvasculature before exploring AI-related chapters. \\
        Clinicians & Focus on imaging modalities, biomarkers, and clinical interpretation. \\
        Students &Read sequentially to establish interdisciplinary foundations. \\
        \bottomrule
    \end{tabularx}
\end{table}

Readers are encouraged to revisit previously covered concepts as their understanding develops, since many topics in retinal imaging are closely interconnected. As this handbook is intended to be a living knowledge base, constructive feedback, corrections, and suggestions for future editions are always welcome. If you identify any inaccuracies, outdated information, or topics that could be improved, please feel free to contact me at \texttt{thanhhuong792000@gmail.com}. Every contribution, no matter how small, is greatly appreciated.